### 2020-06-05 writeup/experiments.tex
writing

We validate our theory and our algorithmic insights.
First, we validate the single-task based metric on sentiment analysis and ChestX-ray14 datasets.
We show that single-task learning results can help predict positive or negative transfer for both datasets.
Second, our proposed incremental training schedule improves the training efficiency of standard multi-task training on sentiment analysis tasks.
%Third, we measure the data efficiency ratio of multi-task learning on six sentiment analysis tasks.
Third, when source/target sample ratio is large, performing the alignment procedure of \cite{WZR20} provides more improvement for MTL.
Finally, we validate our theoretical results on text classification tasks.

>>>>

We validate our theory and algorithmic insights.
First, we validate the single-task based metric on sentiment analysis and ChestX-ray14 datasets.
We show that single-task learning results can help predict positive or negative transfer for both datasets.
Second, our proposed incremental training schedule improves the training efficiency of standard multi-task training on sentiment analysis tasks.
%Third, we measure the data efficiency ratio of multi-task learning on six sentiment analysis tasks.
Third, when the sample ratio is large, performing the alignment procedure of \cite{WZR20} provides more improvement for MTL.
Finally, we validate our theoretical results on text classification tasks.

### 2020-06-05 writeup/intro.tex
writing

\vspace{-0.3in}
\begin{abstract}
\vspace{-0.05in}
%When does multi-task learning provide positive (or negative) information transfer, compared to single-task learning?
	Multi-task learning is a powerful approach in many applications such as image and text classification.
	Yet, there is little rigorous understanding of when multi-task learning performs well, even compared to single-task learning.
	To be precise, we say that multi-task learning provides \textit{positive transfer} if it outperforms single-task learning, or \textit{negative transfer} otherwise.
	In this work, we consider three components including \textit{task similarity}, \textit{sample size} and \textit{covariate shift} to determine transfer effect.
	We study the high-dimensional linear regression setting that allows us to define each component precisely,
% the performance of predicting a particular task given multiple tasks.
%a multi-task learning architecture that uses a shared layer for all tasks and a separate output layer for each task.
	and show that the bias-variance tradeoff of multi-task estimators determines the transfer effect.
%	We analyze the bias-variance tradeoff by developing tight concentration results using random matrix theory.
	%we show that the type of transfer is determined by the bias-variance tradeoff of multi-task learning estimators.
	%We develop a technical tool to analyze the.
%	We develop a technical tool on the inverse of the sum of two random matrices that naturally arises from the analysis.
	Then, we explain three negative effects in multi-task learning including decreased task similarity,	increased source sample size and covariate shift under increased source sample size.
	We validate the three effects on text classification tasks.
	Inspired by our theory, we show two practical connections of interest.
	First, single-task performance can help understand multi-task performance.
	Second, incrementally adding training data can mitigate negative transfer and improve multi-task training efficiency.% for predicting a particular task.
%	We validate our theory and our proposed method .
\end{abstract}

@@

%Multi-task learning is an inductive learning mechanism to improve generalization performance using related task data.
%Many state-of-the-art results in computer vision and natural language processing are obtained using multi-task learning.
Multi-task learning is a powerful approach for improving performance on prediction tasks in computer vision \cite{chexnet17,ZSSGM18}, natural language processing \cite{GLUE,superglue} and many other areas \cite{ZY17}.
%In multi-task learning, having related task data is fundamental to its performance.
%Multi-task learning is particularly powerful when there is limited labeled data for a task to be solved, meanwhile more labeled data from different but related tasks is available.
%By combining multiple information sources, it is possible to share all the information in the same model.
In many settings, multiple data sources are available for predicting a particular target task.
%For example, many applications in , and many other areas have been achieved by learning from multiple tasks together.
The performance of multi-task learning depends on the relationship between the data sources and the target \cite{C97}.
When the data sources are relatively different from each other, negative transfer has often been observed \cite{PY09,AP16,BS17}.
While many empirical approaches have been proposed to mitigate negative transfer \cite{ZY17}, a precise understanding of when negative transfer occurs remains elusive in the literature \cite{R17}.
%This phenomenon, known as \textit{negative transfer}, is fundamental to the understanding of multi-task learning.
In this work, we provide a rigorous study to understand when positive or transfer occurs in the setting of high-dimensional linear regression.
We show that the bias-variance tradeoff of multi-task learning estimators determines the transfer effect, and we develop new concentration bounds to analyze the tradeoff.
%Inspired by the theory, we propose an incremental training schedule to improve multi-task training.
%We consider a setting where the target task has limited labeled data and show
%On the other hand, unless the structures across task data are well-understood, applying multi-task learning on several different datasets often result in suboptimal models (or negative transfer in more technical terms).

Understanding positive versus negative transfer requires developing generalization bounds that scale tightly with properties of each task data such as its sample size.
This presents a technical challenge in the multi-task setting due to the presence of different task features, even for two tasks.
For Rademacher complexity or VC-based techniques, the generalization error scales down as the sample sizes of all tasks increase, when applied to the multi-task setting \cite{B00,AZ05,M06,MPR16,WZR20}.
Without a tight lower bound for multi-task learning, comparing its performance to single-task learning results in vacuous bounds.
From a practical standpoint, developing a better understanding of multi-task learning in terms of properties of task data is important because it is often applied to settings in which a particular task has limited amount of labeled data \cite{RH19}.
%For example, the sample sizes of all tasks are often assumed to be equal \cite{B00,LPTV09,LPVT11}.
%On the other hand, uneven sample sizes (or dominating tasks) have been empirically observed to cause negative transfer \cite{YKGLHF20}.
%The benefit of learning multi-task representations has also been studied for certain half-spaces \cite{} and sparse regression \cite{}.
%When all tasks are sufficiently similar, adding more labeled data improves the generalization performance for predicting a particular task \cite{WZR20}.

%\textbf{Setup and Main Results.}
In this work, we apply recent development from the random matrix theory literature \cite{erdos2017dynamical,isotropic,Anisotropic} to determine transfer effect in the high-dimensional linear regression setting \cite{HMRT19,BLLT20}.
This setting allows us to measure the difference of task data by three components, including \textit{task similarity}, \textit{sample size} and \textit{covariate shift}.
To be precise, we define each component for two tasks below and our definition applies more generally.
We refer to the first task as the source and the second as the target.
\squishlist
	\item \textbf{Task similarity:} Assume that both tasks follow a linear model with parameters $\beta_1, \beta_2\in\real^p$, respectively.
	We measure the distance between them by $\norm{\beta_1 - \beta_2}$.
	\item \textbf{Sample size:} Let $n_1 = \rho_1 \cdot p, n_2 = \rho_2 \cdot p$ be the sample size of each task, where $\rho_1, \rho_2>1$ are both fixed values that do not grow with $p$.
	We measure the source/target sample ratio by $\rho_1 / \rho_2$.
%	Importantly, $\rho_2$ can be a small constant (say $2$) to capture the need for more labeled data.
	\item \textbf{Covariate shift:} Assume that the task features are random vectors with positive semidefinite covariance matrix $\Sigma_1,\Sigma_2\in\real^{p\times p}$, respectively.
	%$x = \Sigma_i^{1/2}z$, where $z\in\real^p$ consists of i.i.d. entries with mean zero and unit variance, and is a positive semidefinite matrix.
	We define covariate shift as the matrix $\Sigma_1^{1/2}\Sigma_2^{-1/2}$.
\squishend

@@

%Let $n_i = \rho_i \cdot p$ denote the data size and $X_i\in\real^{n_i\times p}$ denote the features of task $i$.
%The labels of task $i$ are given by $Y_i = X_i\beta_i + \varepsilon_i$, where $\beta_i\in\real^p$ denotes task $i$'s ground truth parameters and $\varepsilon_i$ denotes i.i.d. random noise with mean zero and variance $\sigma^2$.
We consider a multi-task estimator obtained using a shared linear layer for all tasks and a separate output layer for each task \cite{WZR20}.
This two layer model is inspired by a commonly used idea of hard parameter sharing in multi-task learning \cite{R17,MTDNN19}.
We consider the bias and variance of the multi-task estimator for predicting a particular task, and compare its performance to single-task learning.
%This corresponds to minimizing $ \sum_{i=1}^t \norm{X_i B W_i - Y_i}^2$.
%Let $\hat{\beta}_t^{\MTL}$ denote the optimal multi-task estimator for the target task, which is defined precisely in Section \ref{sec_prelim}.
%We revisit the bias-variance tradeoff of $\hat{\beta}_t^{\MTL}$.

\textbf{Main results.} First, we develop tight bounds for the bias and variance of the multi-task estimator for two tasks.
Since the total sample size has increased, the variance of the multi-task estimator is \textit{always smaller} than that of the single-task estimator.
Since task models are different, the bias of the multi-task estimator is \textit{always larger} than that of the single-task estimator (which is $0$ since $n_1 > p$).
Hence, the tradeoff between bias and variance determines whether the transfer is positive or negative.
We provide a sharp analysis of the variance that scales only with sample size and covariate shift in Lemma \ref{lem_cov_shift_informal} and extend it to the bias.
Combined together, we analyze the bias-variance tradeoff for two tasks in Theorem \ref{thm_main_informal} and extend the analysis to many tasks with same features in Theorem \ref{thm_many_tasks}.
%For the setting of two tasks, we show how the variance of the multi-task estimator  scales with sample size and covariate shift in the following result.
%\textit{Our first contribution} is to develop a concentration bound that arises naturally from the bias-variance tradeoff of $\hat{\beta}_t^{\MTL}$ for two tasks.
%Let $\hat{\beta}_t^{\STL}$ denote the single-task estimator.
%Without loss of generality, let the $t$-th task denote the target task.
%Importantly, the target task's data size is a fixed constant times $p$ in the high-dimensional setting.
%Hence adding more labeled data can help improve its test performance.
%$B\in\real^{p\times r}$
%$\set{W_i \in \real^{r}}_{i=1}^t$

@@

Second, we explain the performance of multi-task learning by varying the three components above in isotropic and covariate shifted settings.
We describe three simulations in Figure \ref{fig_model_shift_phasetrans} for two linear regression tasks and measure the loss of the single-task estimator minus the multi-task estimator.
%We observe that negative transfer occurs as (a) \textit{task similarity}: tasks become more different; (b) \textit{data size}: source/target data size increases.
%\textbf{Task similarity:}
%\textbf{Data sizes:}
%\textbf{Covariate shift:}
%Furthermore, MTL performance is negatively affected when (c) \textit{covariate shift}: the covariance matrices of the two tasks become more different.
\squishlist
	\item We provide a deterministic condition that depends on the sample sizes and model distance in the isotropic setting (Proposition \ref{prop_dist_transition}).
	Our result predicts most of the empirical observations in Figure \ref{fig_model_shift} correctly.
%	It is crucial that the concentration result in Theorem \ref{lem_cov_shift_informal} is sufficiently precise so that we can explain the transition phenomena in Figure \ref{fig_model_shift} and \ref{fig_size}.
	The unexplained observations are caused by an error term that arises from the bias of the multi-task estimator.
	We discuss these in Section \ref{sec_insight} more precisely.
	\item We provide a similar condition that explains a curious phenomenon in Figure \ref{fig_size}, namely adding more labeled data from the source task does not always improve performance (Proposition \ref{prop_data_size}).
	%Theorem \ref{lem_cov_shift_informal} allows us to compare MTL performance under different covariate shifts.
	\item We study a special case of having the same task models and show that MTL is best performing without covariate shift (Proposition \ref{prop_covariate}).
	For this special case, the bound of Lemma \ref{lem_cov_shift_informal} matches the empirical curve in Figure \ref{fig_covariate} accurately.
\squishend
%In Section \ref{sec_insight}, we consider three components including task similarity, data size and covariate shift for a simplified isotropic setting of two tasks.
%We measure task similarity by how small is the distance between $\beta_1$ and $\beta_2$.
%Using our tool, we explain a transition from positive to negative transfer as task similarity decreases.
%		Furthermore, we show that negative transfer is more likely to occur when the source task labels are particularly noisy.
%		In Section \ref{sec_validate}, we validate the observation on text and image classification tasks.
%	In , we provide the trade-off between $\norm{\beta_1 - \beta_2}^2$ and a certain function $\Phi(\rho_1, \rho_2)$ to determine the type of transfer.
%We show that increasing the data size of the source task does not always improve performance for the target task in multi-task learning.
Along the way, we explain a key empirical finding of Taskonomy by Zamir et al. \cite{ZSSGM18}, by analyzing the benefit of MTL for reducing labeled data to achieve comparable performance to STL, .
%We show that covariate shift, measured by $\Sigma_1^{1/2}\Sigma_2^{-1/2}$, is another cause for suboptimal performance for $\hat{\beta}_t^{\MTL}$.
%		We show that as $n_1 / n_2$ becomes large, having no covariate shift between the source and target tasks yields the optimal performance for the target task.
%		On the other hand, when $n_1 / n_2$ is small, there are counter examples where having the same covariance matrix is not necessarily the optimal choice.

Finally, we connect our theory to practical problems of interest.
We provide a single-task based metric to predict positive or negative transfer in multi-task learning.
While it is not well understood when multi-task learning provides positive transfer, we show that the STL results can help indicate and understand MTL results on ChestX-ray14 \cite{chexnet17} and sentiment analysis datasets \cite{LZWDA18}.
Inspired by our observation that adding more source task data does not always improve performance, we propose to train multi-task models by incrementally adding source task data for predicting a target task.
We show that our training schedule reduces the computational cost by $55\%$ compared to baseline multi-task training on the sentiment analysis dataset, while keeping the accuracy the same.
Last, we validate our three theoretical findings on sentiment analysis tasks.

>>>>

\vspace{-0.3in}
\begin{abstract}
\vspace{-0.05in}
%When does multi-task learning provide positive (or negative) information transfer, compared to single-task learning?
	Multi-task learning is a powerful approach in many applications such as image and text classification.
	Yet, there is little rigorous understanding of when multi-task learning performs well, even compared to single-task learning.
	To be precise, we say that multi-task learning provides \textit{positive transfer} if it outperforms single-task learning, or \textit{negative transfer} otherwise.
	In this work, we consider three components including \textit{task similarity}, \textit{sample size}, and \textit{covariate shift} to determine transfer effect.
	We study the high-dimensional linear regression setting that allows us to define each component precisely
% the performance of predicting a particular task given multiple tasks.
%a multi-task learning architecture that uses a shared layer for all tasks and a separate output layer for each task.
	and show that the bias-variance tradeoff of multi-task estimators determines the transfer effect.
%	We analyze the bias-variance tradeoff by developing tight concentration results using random matrix theory.
	%we show that the type of transfer is determined by the bias-variance tradeoff of multi-task learning estimators.
	%We develop a technical tool to analyze the.
%	We develop a technical tool on the inverse of the sum of two random matrices that naturally arises from the analysis.
	Then, we explain three negative effects in multi-task learning including decreased task similarity,	increased source sample size, and covariate shift under increased source sample size.
	We validate the three effects on text classification tasks.
	Inspired by our theory, we show two practical connections of interest.
	First, single-task performance can help understand multi-task performance.
	Second, incrementally adding training data can mitigate negative transfer and improve multi-task training efficiency.% for predicting a particular task.
%	We validate our theory and our proposed method .
\end{abstract}

@@

%Multi-task learning is an inductive learning mechanism to improve generalization performance using related task data.
%Many state-of-the-art results in computer vision and natural language processing are obtained using multi-task learning.
Multi-task learning is a powerful approach for improving performance on prediction tasks in computer vision \cite{chexnet17,ZSSGM18}, natural language processing \cite{GLUE,superglue}, and many other areas \cite{ZY17}.
%In multi-task learning, having related task data is fundamental to its performance.
%Multi-task learning is particularly powerful when there is limited labeled data for a task to be solved, meanwhile more labeled data from different but related tasks is available.
%By combining multiple information sources, it is possible to share all the information in the same model.
In many settings, multiple source tasks are available for predicting a particular target task.
%For example, many applications in , and many other areas have been achieved by learning from multiple tasks together.
The performance of multi-task learning depends on the relationship between the source and target tasks \cite{C97}.
When the data sources are relatively different from each other, negative transfer has often been observed \cite{PY09,AP16,BS17}.
While many empirical approaches have been proposed to mitigate negative transfer \cite{ZY17}, a precise understanding of when negative transfer occurs remains elusive in the literature \cite{R17}.
%This phenomenon, known as \textit{negative transfer}, is fundamental to the understanding of multi-task learning.
In this work, we provide a rigorous study to understand when positive or negative transfer occurs in the setting of high-dimensional linear regression.
We show that the bias-variance tradeoff of multi-task learning estimators determines the transfer effect, and develop new concentration bounds to analyze the tradeoff.
%Inspired by the theory, we propose an incremental training schedule to improve multi-task training.
%We consider a setting where the target task has limited labeled data and show
%On the other hand, unless the structures across task data are well-understood, applying multi-task learning on several different datasets often result in suboptimal models (or negative transfer in more technical terms).

Understanding positive versus negative transfer requires developing generalization bounds that scale tightly with properties of each task data such as its sample size.
This presents a technical challenge in the multi-task setting due to the presence of different task features, even for two tasks.
For Rademacher complexity or VC-based techniques, the generalization error scales down as the sample sizes of all tasks increase, when applied to the multi-task setting \cite{B00,AZ05,M06,MPR16,WZR20}.
Without a tight lower bound for multi-task learning, comparing its performance to single-task learning results in vacuous bounds.
From a practical standpoint, developing a better understanding of multi-task learning in terms of properties of task data is important because it is often applied to settings in which a particular task has a limited amount of samples \cite{RH19}.
%For example, the sample sizes of all tasks are often assumed to be equal \cite{B00,LPTV09,LPVT11}.
%On the other hand, uneven sample sizes (or dominating tasks) have been empirically observed to cause negative transfer \cite{YKGLHF20}.
%The benefit of learning multi-task representations has also been studied for certain half-spaces \cite{} and sparse regression \cite{}.
%When all tasks are sufficiently similar, adding more labeled data improves the generalization performance for predicting a particular task \cite{WZR20}.

%\textbf{Setup and Main Results.}
In this work, we apply recent development from the random matrix theory literature \cite{erdos2017dynamical,isotropic,Anisotropic} to determine transfer effect in the high-dimensional linear regression setting \cite{HMRT19,BLLT20}.
This setting allows us to measure the difference of task data by three components, including \textit{task similarity}, \textit{sample size}, and \textit{covariate shift}.
To be precise, we define each component for two tasks below and our definition applies more generally.
We refer to the first task as the source and the second as the target.
\squishlist
	\item \textbf{Task similarity:} Assume that both tasks follow a linear model with parameters $\beta_1, \beta_2\in\real^p$, respectively.
	We measure the distance between them by $\norm{\beta_1 - \beta_2}$.
	\item \textbf{Sample size:} Let $n_1 = \rho_1 \cdot p, n_2 = \rho_2 \cdot p$ be the sample size of each task, where $\rho_1, \rho_2>1$ are both fixed values that do not grow with $p$.
	We measure the source/target sample ratio by $\rho_1 / \rho_2$.
%	Importantly, $\rho_2$ can be a small constant (say $2$) to capture the need for more labeled data.
	\item \textbf{Covariate shift:} Assume that the task features are random vectors with positive semidefinite covariance matrix $\Sigma_1,\Sigma_2\in\real^{p\times p}$, respectively.
	%$x = \Sigma_i^{1/2}z$, where $z\in\real^p$ consists of i.i.d. entries with mean zero and unit variance, and is a positive semidefinite matrix.
	We define covariate shift as the matrix $\Sigma_1^{1/2}\Sigma_2^{-1/2}$.
\squishend

@@

%Let $n_i = \rho_i \cdot p$ denote the data size and $X_i\in\real^{n_i\times p}$ denote the features of task $i$.
%The labels of task $i$ are given by $Y_i = X_i\beta_i + \varepsilon_i$, where $\beta_i\in\real^p$ denotes task $i$'s ground truth parameters and $\varepsilon_i$ denotes i.i.d. random noise with mean zero and variance $\sigma^2$.
We consider a multi-task estimator obtained using a shared linear layer for all tasks and a separate output layer for each task \cite{WZR20}.
This two-layer model is inspired by a commonly used idea of hard parameter sharing in multi-task learning \cite{R17,MTDNN19}.
We consider the bias and variance of the multi-task estimator for predicting a particular task and compare its performance to single-task learning.
%This corresponds to minimizing $ \sum_{i=1}^t \norm{X_i B W_i - Y_i}^2$.
%Let $\hat{\beta}_t^{\MTL}$ denote the optimal multi-task estimator for the target task, which is defined precisely in Section \ref{sec_prelim}.
%We revisit the bias-variance tradeoff of $\hat{\beta}_t^{\MTL}$.

\textbf{Main results.} First, we develop tight bounds for the bias and variance of the multi-task estimator for two tasks.
Since the total sample size has increased, the variance of the multi-task estimator is \textit{always smaller} than that of the single-task estimator.
Since task models are different, the bias of the multi-task estimator is \textit{always larger} than that of the single-task estimator (which is $0$ since $n_1 > p$).
Hence, the tradeoff between bias and variance determines whether the transfer is positive or negative.
We provide a sharp analysis of the variance that scales only with sample size and covariate shift in Lemma \ref{lem_cov_shift_informal} and extend it to the bias.
Combining both, we analyze the bias-variance tradeoff for two tasks in Theorem \ref{thm_main_informal} and extend the analysis to many tasks with the same features in Theorem \ref{thm_many_tasks}.
%For the setting of two tasks, we show how the variance of the multi-task estimator  scales with sample size and covariate shift in the following result.
%\textit{Our first contribution} is to develop a concentration bound that arises naturally from the bias-variance tradeoff of $\hat{\beta}_t^{\MTL}$ for two tasks.
%Let $\hat{\beta}_t^{\STL}$ denote the single-task estimator.
%Without loss of generality, let the $t$-th task denote the target task.
%Importantly, the target task's data size is a fixed constant times $p$ in the high-dimensional setting.
%Hence adding more labeled data can help improve its test performance.
%$B\in\real^{p\times r}$
%$\set{W_i \in \real^{r}}_{i=1}^t$

@@

Second, we explain the performance of multi-task learning by varying the three components above in isotropic and covariate shifted settings.
We describe three simulations in Figure \ref{fig_model_shift_phasetrans} for two linear regression tasks and measure the loss of the single-task estimator minus the multi-task estimator.
%We observe that negative transfer occurs as (a) \textit{task similarity}: tasks become more different; (b) \textit{data size}: source/target data size increases.
%\textbf{Task similarity:}
%\textbf{Data sizes:}
%\textbf{Covariate shift:}
%Furthermore, MTL performance is negatively affected when (c) \textit{covariate shift}: the covariance matrices of the two tasks become more different.
\squishlist
	\item We provide a deterministic condition that depends on the sample sizes and model distance in the isotropic setting (Proposition \ref{prop_dist_transition}).
	Our result predicts most of the empirical observations in Figure \ref{fig_model_shift} correctly.
%	It is crucial that the concentration result in Theorem \ref{lem_cov_shift_informal} is sufficiently precise so that we can explain the transition phenomena in Figure \ref{fig_model_shift} and \ref{fig_size}.
	The unexplained observations are caused by an error term that arises from the bias of the multi-task estimator.
	We discuss these in Section \ref{sec_insight} more precisely.
	\item We provide a similar condition that explains a curious phenomenon in Figure \ref{fig_size}, namely adding more labeled data from the source task does not always improve performance (Proposition \ref{prop_data_size}).
	%Theorem \ref{lem_cov_shift_informal} allows us to compare MTL performance under different covariate shifts.
	\item We study a special case of having the same task models and show that MTL  performs best without covariate shift (Proposition \ref{prop_covariate}).
	For this special case, the bound of Lemma \ref{lem_cov_shift_informal} matches the empirical curve in Figure \ref{fig_covariate} accurately.
\squishend
%In Section \ref{sec_insight}, we consider three components including task similarity, data size and covariate shift for a simplified isotropic setting of two tasks.
%We measure task similarity by how small is the distance between $\beta_1$ and $\beta_2$.
%Using our tool, we explain a transition from positive to negative transfer as task similarity decreases.
%		Furthermore, we show that negative transfer is more likely to occur when the source task labels are particularly noisy.
%		In Section \ref{sec_validate}, we validate the observation on text and image classification tasks.
%	In , we provide the trade-off between $\norm{\beta_1 - \beta_2}^2$ and a certain function $\Phi(\rho_1, \rho_2)$ to determine the type of transfer.
%We show that increasing the data size of the source task does not always improve performance for the target task in multi-task learning.
Along the way, we explain a key empirical finding of Taskonomy by Zamir et al. \cite{ZSSGM18}, by analyzing the benefit of MTL for reducing labeled data to achieve comparable performance to STL, .
%We show that covariate shift, measured by $\Sigma_1^{1/2}\Sigma_2^{-1/2}$, is another cause for suboptimal performance for $\hat{\beta}_t^{\MTL}$.
%		We show that as $n_1 / n_2$ becomes large, having no covariate shift between the source and target tasks yields the optimal performance for the target task.
%		On the other hand, when $n_1 / n_2$ is small, there are counter examples where having the same covariance matrix is not necessarily the optimal choice.

Finally, we connect our theory to practical problems of interest.
We provide a single-task based metric to predict positive or negative transfer in multi-task learning.
While it is not well understood when multi-task learning provides positive transfer, we show that the STL results can help indicate and understand MTL results on ChestX-ray14 \cite{chexnet17} and sentiment analysis datasets \cite{LZWDA18}.
Inspired by our observation that adding more source task data does not always improve performance, we propose to train multi-task models by incrementally adding source task data for predicting a target task.
We show that our training schedule reduces the computational cost by $55\%$ compared to baseline multi-task training on the sentiment analysis dataset while keeping the accuracy the same.
Last, we validate our three theoretical findings on sentiment analysis tasks.

### 2020-06-05 writeup/setup.tex
writing

We begin by defining our problem setup including the multi-task estimator we study.
Then, we describe the bias-variance tradeoff of the multi-task estimator, and connect the bias and variance of the estimator to \textit{task model distance}, \textit{sample size} and \textit{covariate shift}.
%Finally, we show a tight concentration bound for the bias and variance quantities using random matrix theory.

>>>>

We begin by defining our problem setup including the multi-task estimator we study.
Then, we describe the bias-variance tradeoff of the multi-task estimator and connect the bias and variance of the estimator to \textit{task model distance}, \textit{sample size}, and \textit{covariate shift}.
%Finally, we show a tight concentration bound for the bias and variance quantities using random matrix theory.

### 2020-06-05 writeup/transfer.tex
writing

%We provide precise explanations to the phenomena of negative transfer in multi-task learning.
We provide tight bounds on the bias and variance of the multi-task estimator for two tasks.
We show theoretical implications for understanding the performance of multi-task learning.
(a) \textit{Task similarity}: we explain the phenomenon of negative transfer precisely as task models become different.
(b) \textit{Sample size}: we further explain a curious phenomenon where increasing the source sample size helps initially, but hurts eventually.
(c) \textit{Covariate shift}: as source sample size increases, we show that covariate shift worsens the performance of the multi-task estimator.
Finally, we extend our result from two tasks to many tasks with the same features.
%We explain from three perspectives, including \textit{task similarity}, \textit{sample size} and \textit{covariate shift}.
%We show how negative transfer occurs by varying task similarity or sample size.
%Then we show that when source task sample size becomes large, covariate shift causes more negative effects.

>>>>

%We provide precise explanations to the phenomena of negative transfer in multi-task learning.
We provide tight bounds on the bias and variance of the multi-task estimator for two tasks.
We show theoretical implications for understanding the performance of multi-task learning.
(a) \textit{Task similarity}: we explain the phenomenon of negative transfer precisely as task models become different.
(b) \textit{Sample size}: we further explain a curious phenomenon where increasing the source sample size helps initially, but hurts eventually.
(c) \textit{Covariate shift}: as the source sample size increases, we show that the covariate shift worsens the performance of the multi-task estimator.
Finally, we extend our results from two tasks to many tasks with the same features.
%We explain from three perspectives, including \textit{task similarity}, \textit{sample size} and \textit{covariate shift}.
%We show how negative transfer occurs by varying task similarity or sample size.
%Then we show that when source task sample size becomes large, covariate shift causes more negative effects.
